Appendix to 'Detecting social information in a dense database of infants’ natural

### 2022-01-06 paper/preprint/manuscript_dec2021_apa_blinded.Rmd
add motor development section

## Variation with motor development
In a set of exploratory analyses, we examined how the onset of sitting, cruising, and walking in each individual child changed the proportion of faces and hands in view. Each parent completed the Ages and Stages Questionnaire (ASQ), and we coded the age at which each child reached each motor milestone. To do so, we used a mixed-effects regression with per-child random intercepts

We next examine whether the SAYcam participants' age of reaching particular developmental milestones (sitting, cruising, and walking) significantly influenced the amount of hands or faces that they saw, using a mixed-effects regression with per-child random intercepts.
[table with each child's age of onset per milestone?]

>>>>

## Variability with motor development milestones
How does the social information in view change as a function of motor development? One idea is that children’s ability to stand and move on their own may fundamentally change the visual social information that they see (e.g., facial expressions, gaze cues, pointing)  [@walle2016infant] relative to infants who are still sitting and crawling.  Indeed, in in-lab studies, research has found that children's in-the-moment posture -- and that of their caregiver -- is a strong predictor of the visual social information in view [@franchak2017see; @long2021automated].

We thus next analyzed how the social information in view changed as a function of each child reaching particular developmental motor milestones. Each parent completed the Ages and Stages Questionnaire (ASQ) [@bricker1999ages], which includes questions about their child's motor abilities, and we used the responses from this questionnaire to code the age (in months) at which each child became able to sit, cruise, and walk on their own (questions about crawling were not included in the questionnaire)..  We found considerable variability in the age at which each child achieved these three milestones. Participants S and A were already able to sit at 6 months of age, while Y began achieving this milestone at 8 months. A was able to cruise at 9 months of age, while S reached that milestone at 10 months, with Y just behind. Learning to walk showed the most variation, with S walking after 10 months, A after 13 months, and Y after 16 months of age.

We then used a discontinuity analysis to estimate whether the onset of each of these three motor milestones changed the proportion of faces/hands in each chid's view. Specifically, we used mixed-effects regressions with per-child random intercepts to estimate whether children's age (in months), each motor milestone, and their interaction significantly influenced the proportion of hands or faces that each child saw; see Appendix for tables with full model specifications and tables with all coefficients. Overall, we found that the age at which these children began sitting did not significantly predict changes in either the amount of faces or hands that they saw. However, as children became able to cruise, they saw significantly more faces ($\beta = 0.27$) and hands ($\beta = 0.26$), suggesting that the ability to be upright and locomote even somewhat independently was sufficient to significantly change children's visual social environment. For faces, however, there was also a significant negative interaction of age and cruising ($\beta = -0.03$, $p=0.025$), and a marginal positive effect of age ($\beta = 0.03$, $p=0.055$). However, we did not find major differences with the onset of walking; as these children became able to walk, they saw marginally more hands ($\beta = 0.09$, $p=0.052$). Thus, these analyses confirm and extend cross-sectional finding, leveraging dense, within-child data to help elucidate the complex relationship between motor development and the social information in view.
